Accessories dominate the costs of producing seed

### 2016-10-10 ms/Accessory/ms-supp.Rnw
Option to turn off graphs

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv",
  stringsAsFactors=FALSE, check.names=FALSE)

@@

@

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Conospermum ericifolium}}
\label{fig:map Conospermum ericifolium}
\end{figure}

>>>>

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv",
  stringsAsFactors=FALSE, check.names=FALSE)
flowering_parts$method <- gsub("_", " ", flowering_parts$method, fixed=TRUE)

@@

plot_graph <- function(graph) {

  #plot(graph)
  plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE)
}
@

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot_graph(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot_graph(COER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Conospermum ericifolium}}
\label{fig:map Conospermum ericifolium}
\end{figure}
